---
title: "Symbolic Sponsorship CCES"
output:
  pdf_document: default
  html_document:
    df_print: paged
---



```{r, echo = FALSE, include=FALSE}
library(tidyverse)
library(haven)
library(lme4)
library(sjPlot)
library(ggthemes)
library(rstanarm)
library(marginaleffects)
library(stargazer)
#library(lmerTest)

set.seed(1234)

load(file = "CES_SymbolicLegislation.rda")
ces$inc_approve_cent<- ces$inc_approve - mean(ces$inc_approve)

ces$college<- NA
ces$college[ces$educ >= 5]<- "college"
ces$college[ces$educ <= 4]<- "no college"

ces$LogBillSpons<- log(ces$BillsSpons + 1)

#ces<- ces %>%
#  sample_n(16000)

```



Basic Model: 

Varying slopes and intercepts by each congressional district year. 


Level 1 (Individual level):
$$Y_{ij} = \beta_{0j} + \beta_{1j}PartisanAlignment_{ij} + \epsilon_{ij}$$
Level 2 (District-Year level):
$$\beta_{0j} = \gamma_{00} + \gamma_{01} Bills_{j} + u_{0j}$$
$$\beta_{1j} = \gamma_{10} + \gamma_{11}BillsSpons_{j} + u_{1j}$$


```{r, include = FALSE}

mod1 <- lmer(inc_approve ~ 1 + BillsSpons * party_match + (1 + party_match | dist_year),
                    data = ces, 
                    REML = FALSE,
                    control = lmerControl(optimizer = "bobyqa",
                                        optCtrl = list(maxfun = 1000)))
#summary(mod1)

```




Graphs of Bill Sponsorship interacted with Partisanship

```{r, echo = FALSE}
##Predicted values

graph1<- plot_model(mod1, type = "pred", terms = c("BillsSpons", "party_match")) +
  theme_tufte() + 
  ggtitle("Predicted Voter Approval of MC") + 
  xlab("Bills Sponsored") + 
  ylab("Approval") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(color = "Party Match") 
print(graph1)


# Plot interaction effects
graph2<- marginaleffects::plot_slopes(mod1, variables = "BillsSpons", condition = "party_match",
                                      re.form = NA) + 
  theme_tufte() + 
  ggtitle("Marginal Effects of Bills Sponsored on Approval") + 
  xlab("") + 
  ylab("Marginal Effects of Bills Sponsored") + 
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5)
print(graph2)

```




```{r, include = FALSE}

modIss <- lmer(inc_approve ~ 1 + BillsSpons * IssueAgree  + (1 + IssueAgree | dist_year),
                    data = ces, 
                    REML = FALSE,
                    control = lmerControl(optimizer = "bobyqa",
                                        optCtrl = list(maxfun = 1000)))
summary(modIss)


graphAgree<- marginaleffects::plot_slopes(modIss, variables = "BillsSpons", condition = "IssueAgree",
                                      re.form = NA) + 
  theme_tufte() + 
  ggtitle("Marginal Effects of Bills Sponsored on Approval Over Issue Agreement") + 
  xlab("") + 
  ylab("Marginal Effects of Bills Sponsored") + 
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5)
print(graphAgree)


```

```{r}
graphAgreePred<- plot_model(modIss, type = "int", terms = c("BillsSpons", "IssueAgree"),
                            group.terms = c(-1, 0, 1)) +
  theme_tufte() + 
  ggtitle("Predicted Voter Approval of MC") + 
  xlab("Bills Sponsored") + 
  ylab("Approval") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(color = "Issue Agreement") 
print(graphAgreePred)

```








```{r}
modAgreeParty <- lmer(inc_approve ~ 1 + BillsSpons * IssueAgree + BillsSpons * party_match + (1 + party_match | dist_year),
                    data = ces, 
                    REML = FALSE,
                    control = lmerControl(optimizer = "bobyqa",
                                        optCtrl = list(maxfun = 1000)))
summary(modAgreeParty)

```


```{r}
modAgreePartyRob <- lmer(inc_approve ~ 1 + LogBillSpons * IssueAgree + LogBillSpons * party_match + (1 + party_match | dist_year),
                    data = ces, 
                    REML = FALSE,
                    control = lmerControl(optimizer = "bobyqa",
                                        optCtrl = list(maxfun = 1000)))
summary(modAgreePartyRob)

```

```{r}
cesSame<- ces %>%
  filter(party_match == "Same Party")

modSameAgree <- lmer(inc_approve ~ 1 + BillsSpons * IssueAgree +  
                       (1 + IssueAgree | dist_year),
                    data = cesSame, 
                    REML = FALSE,
                    control = lmerControl(optimizer = "bobyqa",
                                        optCtrl = list(maxfun = 1000)))
summary(modSameAgree)


```

```{r}
graphSameAgree<- marginaleffects::plot_slopes(modSameAgree, variables = "BillsSpon", condition = "IssueAgree",
                                      re.form = NA) + 
  theme_tufte() + 
  ggtitle("Marginal Effects of Bills Sponsored on Approval Over Issue Agreement for Same Party") + 
  xlab("") + 
  ylab("Marginal Effects of Bills Sponsored") + 
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5)
print(graphSameAgree)
```
















Subscript Notation Explanation

Variable Definitions: 

$Y_{i(j)}$: Incumbent approval rating for individual i in district-year j
$(BillsSpons)_{j}$: Number of bills sponsored by the incumbent in district-year j (Level 2)
$(party_match)_{i(j)}$: Party match for individual i in district-year j (Level 1)
$\epsilon_{i(j)}$: Random error for individual i in district-year j
$u_{0j}$: Random intercept for district-year j
$u_{1j}$: Random slope for district-year j

Model Parameters:

$\gamma_{00}$: Overall intercept
$\gamma_{01}$: Effect of bills sponsored (Level 2)
$\gamma_{10}$: Effect of partisan alignment (Level 1)
$\gamma_{11}$: Cross-level interaction effect


Combined Model:
$$Y_{i(j)} = \gamma_{00} + \gamma_{01}(\text{BillsSpons}){j} + \gamma{10}(\text{party_match}){i(j)} + \gamma{11}(\text{BillsSpons}){j}(\text{party_match}){i(j)} + u_{0j} + u_{1j}(\text{party_match}){i(j)} + \epsilon{i(j)}$$

